\chapstory{Andy Dibble}{The Search for Sky}

The forefather of our clan came of age and sought Sky, vowing not to
return until he found it. The gods knew the man was as tenacious as a
falling stone. Each boasted to the others, ``I'll be the one to dissuade
him.''

With only his shadow to measure himself against, the man climbed into a
high cavern. Gales blustered remorselessly. Against the downpour, the
ceiling was just a sieve.

``Turn back!'' the god Gush howled from the storm.

``Is this Sky?''

The storm howled laughter. ``Abandon your search, and I will give you a
boat that will carry you along any river no matter rapids, falls, or the
crush of a cavern ceiling.''

``I swore-''

``I know what you swore! But see how you plod. You will never find Sky
by walking.''

``But I'll walk on.''

Gush bellowed torrentially. The man barely escaped the flood.

He entered a new cave, one teaming with moss rose, hedgehogs, and
leftover rain. There he found the goddess Maya with her eighteen
diaphanous handmaidens. She wore a royal blue gown that flowed over the
lichen-carpet.

``Are you Sky?''

``Me? No, but if you give up your search and stay with me, I will bear
you children.''

``I'll settle down when I find Sky.''

``But Sky is too far away for you to find, even if you walked your
entire life. Only your children will have enough years to find Sky.''

``So I will fail if I go on or if I stay?''

``I'm afraid so. But if you stay, I am yours and Sky remains for your
children.''

``I must go as I swore I would.''

The man roamed on, but his way contracted into a warren of the
luminaries. They lived when the world was young, when no one had to
migrate.

He found three wonders: a lantern whose light turns stone into glass, a
prism that sprays darkness, and lenses keen enough to spy the sigaldry
on the husks of seeds. But none were Sky.

A crone appeared to him. One gimlet eye glinted in her shriveled head,
squinting, just half-open. Her cloak was a map of the world: rivers
cascading from the collar, always through caves, caves upon caves, a
rippling mosaic. But its lower hem was torn away.

``Who are you?''

``A seeker, like yourself.'' Her voice echoed like his voice.

``Are you going to offer me something?''

``You won't stop, even when I do. But just to tease you, I'll tell you
where Sky is if you stop searching. Then you can tell another where to
look.''

``I swore---''

``I know.'' Her eye only half-opened as she winked. ``Some advice, boy.
\emph{Beware a written word}.''

He formed a question, but she waved him on, ``Go on, go on.''

The man slipped down, to the nether regions near the Downsea. Here a
battle had raged among cimmerians and troglodytes just hours ago. Vermin
and every kind of insect swarmed through the fresh carrion.

The one soldier standing turned to him and said, ``This is not Sky,
recruit.'' Blood stained the soldier's brow and cheeks. But it was not
his blood.

``This could never be Sky, Toutatis.''

``Renounce your search, and I promise you will never be defeated and be
always the one left standing.''

``Giving up would be its own defeat.''

``Your choice is to be a victor or a corpse! Sky is held from you.''

``Let me be a corpse that sought Sky, rather than a victor standing
alone among corpses.''

Down he went, the Downsea lapping on his side. For all its brine and
sleepless tugging, the sea did not erode the shore. Perfect in pallor it
was, inert, unlistening. It would take no seed. Ashes twined snake-like
in the keening wind. There he met Hood, skeleton-thin, robed in white,
face swallowed in shadow.

``Let me pass,'' the man said.

``We don't have to be enemies, if you only give up your search. If you
turn back, I give you your life always, and you will never die.''

``We will always be enemies, you and I.''

``But Sky is much too far away to find in the span allotted to you.
Seize eternal life while I offer it.''

``So I fail if I go or if I turn back.''

Hood's chuckle was bones scraping together.

The man climbed and came to a vital string of caves, thriving with
amaranth, blackberries, and yams. He dug wrist-deep in the chill dark
loam. It smelled of cumin.

A voice rumbled from the land itself, ``Your goal is accomplished.''

``This is Sky?'' the man said in awe.

``No, but here you will never need to migrate.''

Cropseed would not turn this place wan for ten generations. But the
eleventh or twelfth would have to move on.

He turned his back.

``You ask too much, son of man. This is the closest to Sky you will ever
come.''

The man did not believe the rumbler, but he camped in his plenty.

That slinking whisperer, Nafs, came to him in a dream. His harlequin
outfit was sewn with sheeny buttons, and he wore a mask of ivory. The
man suspected he grinned beneath the mask.

``Give up on Sky, and I'll make it worth your while.''

``You're Nafs, just an old liar. Why should I believe you?''

``Because I'll give you the boon you need to find it. You will always
know truth from lies.''

The man woke from the dream. He turned his back again.

Nafs flit to a broad cavern along the man's path, so vast even the light
of a thousand lanterns would be lost seeking a far side, a cave
exteriorized, supernal, flung with an alien blue.

The man reached that broad cavern and spied a marker above the entrance.
It read: ``Sky.'' He went to tell his clan of his success.
