\chapstory{Bhim Nimgade}{Luc and Beto at\\ The End of the World}

``I'm just not sure, so not sure, not sure at all. Oh Mercy Me, I have
no surety. Where this piece comes from, and where it goes, and how it
fits in, and where it all goes in the end, I just don't know. And how it
ends, I just don't know.'' Luc looked up into the heavens, and then
lowered his head to look at his companion.

Beto said, ``Oh, Pish Tosh, the world's not going to end just now. It
just seems so. And if you think of something else, well then, things are
right again, things are right as rain. Just hold on, hold on to that
caprice, and there you have it. World - not ending. World without end.''

Luc and Beto sat at the flimsy table, careful not to put too much weight
on it, not to even let their plates rest on it too long.

``It's best to hold on to your plate,'' said Luc. So they both did.
Holding the plate in one hand and wielding the plasticware with the
other. It took attention, it did.

``Beto, you're the lucky one. Always have been. You could get away with
putting the plate on the table, if you want.''

Beto had taken a big bite of sauerkraut, and he held up his plastic fork
in the air as if to command or request a pause to let him finish the
bite, and then speak. He chewed, and chewed some more, and he swallowed;
and then he grunted.

Luc had been leaning forward in his chair, balancing his plate
carefully, and now he leaned back again. ``That's it, then? That's it? I
thought you were going to say something.''

``Why would I want to say something? I'm eating my sauerkraut, ersatz
sauerkraut as it may be, but there it is. Eating and holding my plate.
As you said we should.''

``There, you said something. Was that what you had wanted to say, maybe?
Your action belies your statement - though I mean your action IS your
statement - you stated that you WOULDN'T be stating something -''

``No, I only questioned why I have to speak when you tell me to. I'm not
a dog.''

``Dogs don't speak. Oh, OK, we do say `Speak' to a dog, in the
performance of a threadbare parlor trick, but the intent is
metaphorical, is it not?''

``Will you let me eat my plate in peace?''

``You're the one who was going to speak, and I waited, and I waited, and
it was like the old saying, `the elephant labored, and gave birth to a
mouse'. Hardly worth it, I say. Hardly worth it.''

``You would do better to stop the labored metaphors, and leave me to my
plate of comestibles. It's getting cold.''

``It started out cold. If anything, it's warming up, coming to room
temperature. And it's not that good, is it. Not the delectable viands of
a proper House of the Second Order.''

``Proper, Proper. What manner of Proper is this? It's plastic plates,
and plastic forks. Not even plastic knives and plastic spoons - oh no,
it's all forks only, which dig into the flimsy plastic plates, and so
the brine runs out and drips onto our table or onto our knees, or worse
yet, onto our pants-crotches, which is very disagreeable indeed. No
plastic spoons to ladle up the brine, no plastic knives to cut up the
kraut, no bread to soak up the brine, it's all just a big mess.''

``Well, you're saying a lot, for a fellow who said `I'm not a dog.'\,''

``That's neither here nor there. It's true, I'm not a dog. Not by any
stretch of the imagination. Would a dog eat from a plastic plate, with a
plastic fork, eating these miserable mushy je-ne-sais-quois?''

Luc said, ``Fine, fine, who's belaboring metaphors now? Let go of the
dog. The dog doesn't really matter. We're at the end of the world, or
damn near it.''

``If it's the end of the world, we really shouldn't be arguing, should
we? And even if we would want to argue, shouldn't we argue about big
things, like portents, and divinations, and art, and death?''

``Who's arguing? I, arguably, just wanted to hear what you were about to
say, or that you looked like you were about to say. One might say, I was
in consonance with your thought, or with your pre-meditative thought,
however aborted and botched it might have been in its breaching the air
in its birthing moments.''

``Okay, now, who's belaboring what? I just wanted to have my bite in
peace. Maybe, we'll live to tell the tale, and maybe not. You've gotten
the idea that the world is going to end, or is coming to an end, which I
think is the same thing. Luc, I am granting your premise, for the sake
of argument - but by Jove, I am not interested in an argument. I would
rather have pastries of various sorts, with fine cups of hot seaweed
tea. I would rather have fronds of chewy kelp, and roasted carrots. Have
you seen that type of guillotine that people have, for cutting bagels,
without injuring oneself? I would want one of those, and a toaster, so I
could have myself a fine toasted bagel with a thin veneer of marmite. I
could do very well with such things, and that would stave off any
unpleasant ruminations on the end of the world, which would include our
own lives and discussions. Given that the world is going to end - and
mind you, I am just going along with your fantasy and fugue in some
minor and melancholy vein, though I reserve the right to at any moment
spring out of it and go back to thinking that the world will continue as
such, and I'll defend to the death my right to hold on to such a thought
-''

``Beto, Beto; for one who wishes to wave others into silence, and then
sit in silence himself, you are being remarkably logorrheic. And you
think much of food. I can imagine you tucked away in a little
hibernaculum, waiting for the end of the world to just kind of blow
over, like winter, and then you would stumble out, sleepily,
ill-tempered, emaciated, and you would see me and begin to argue that I
was totally wrong, and that the world has NOT in fact ended.''

``Luc, I would emerge because I had steadfastly held in my mind the
conceit that the world will continue, through the rhythms of the
seasons, the tides of life, the songs of the manatees. And you, my
friend, would have ceased to exist, because your mind, in its stubborn
and steadfast grip on the world-ending conceit, would have caused your
own very existence to cease and desist. Fancy that!''

``Your logic is impeccable, at least at first glance, or first
rumination; I cannot poke holes in it. So you would exist, and go on
without me. I would wither, and dissolve, and blow away in the wind. I
am not so enamored of that end. But then, if it is to be, then how bad
would it be? I would know nothing of the world going on, once I had
departed. So I would scarce miss it, would I?''

``Luc, true, we do not often think of the end of our powers of cognition
and perception. Or at least not dispassionately. It may be a meditation
that leads to vast insights. Doors into other realms.''

``These chairs, though they be unthoughtfully made, are solid enough,
and hold our weight. The table, though, is hardly worth the appellation.
Is there a clue, there, as to the nature of things?''

``And where is my plate? My lucky plate? I was not finished with my
meal, unsatisfactory as it was. And now it's gone. I sit here without
plate, without fork, without my meal - what the devil was it, I can't
rightly remember now.''

``Ah, Beto, you were so intent on that bite, that you were snapping at
me for perhaps interrupting it. What matters that bite now? You could
have eaten it, or not eaten it. It is all the same now. One bite closer
to the end of the world.''

``Platitude-mouthing Fool! That could be said for every bite, or any
bite, from the very beginning of the world, to the end of it. To the
bitter, bitter end.''

``Spout insults as you like, it changes nothing. Our food was bland;
briny, but insipid. Hardly bitter. What a bland, bland end!''

``I prefer to think of it as a bland\ldots{} as a bland\ldots{}. Well,
continuation. My way is better. For a bland middle is not so sad as a
bland ending.''

``If we are not at the end of the world, then where are our plates? We
had our plates, flimsy as they were, but they were ours, they were in
our hands, and we could eat off of them. We had our food\ldots{}''

``And do you remember our food, do you?''

And they sat there in silence, their words suddenly turned off. There
had been food, had there not? There had been plates. There had been so
much...
