\chapstory{Bhim Nimgade}{The Reading Room}

\lettrine{T}{hrough the night,} Helward could hear the faint murmurs and tapping
coming from the reading room. And the creaking of floor boards, the
rustling of crinoline and the fluttering of paper; the heavy thuds of
downfalling books, the stertorous breathing, the sharp yips of
discomfort. Did he sleep with one eye open? Not quite. He had drifted
into half sleep at some point during the night, reading about obdurate
English people arguing interminably and at a muted distance about
obscure points regarding people he knew little about. He had intended to
go on reading, grimly, until he got to the good parts. Surely these
people would tire of this petty discourse and actually have sex with
each other. But it all did seem to go on and on with little progress
toward those consummations that he so devoutly desired. And so he nodded
off from time to time, waking again to cast an eye upon their slow
progress across the pages, and wondering glumly if even their sexual
dalliances might not serve to interrupt their tedious soliloquies and
humdrum petty conversations. And thus he found himself, through the
night, stalking halfway between this world and the world of the book,
\emph{A Midsummer Night's Lechery}. So promising the title!

There were not supposed to be sounds coming from the reading room. He
would go and investigate. On his head a nightcap, in his hand a candle,
and under his arm tucked the book, he rose from his tousled bed and - he
found himself still rising. He was a foot above the floor, with the
candle throwing flickering shadows about him.

"Well, this makes things convenient," he said, or he thought he said.
Those who rise at night often come down with a crash, what with throw
rugs and sharp-edged toys strewn about---ah the dangers of balls and
jacks when so casually stepped on---and of course the dreaded wandering
coffee tables. Doubtless there were shoe horns, doll heads, milk trucks,
railroad trestles, and empty matchboxes; bits of dog food---both dry and
wet---and vagrant electrical cords. But now, he was above all this. He
moved, in a gliding sort of way, toward the bedroom door, and then out
into the hallway, and on to the reading room.

Light was coming from under the heavy door into the dark hallway. He
pushed the door open, slowly, and peered in. There was a low fire in the
fireplace, and among all the books and shadows in the room, he began to
be able to see a number of pale, lovely women, in their nightgowns,
turning to look at him with their solemn eyes.

"Where have you been," said one, as she lazily pushed a book along the
top of a desk, until it reached the edge and then fell onto the floor.
He started at the sound, and they smiled and giggled.

"Come in," she said. And she beckoned, with a shimmering finger, and he
felt himself quiver and float silently toward her.
