\chapstory{Bhim Nimgade}{Flying From This World}

The fabric of this world is getting thinner and thinner and it cannot
hold me much longer.

I speak less and less to this world.

The poet has said, Untongued, I turned to still forgetting all I am.
Yes, Ursula knew about that journey that I am about to embark upon.

When the day has crept away, and all of you have gone, I am still here,
alone. And my pillow, eyeless and without pity, gazes upon me at night.
My pillow murmurs about the road to come, and I listen.

At night, the planets and the stars come to the window, swimming and
shivering on the heaving sea, and look in on me. I count the stars, and
there are too many. I count the planets; and when I come to the ninth
planet, the planet of magicians, I know they look at me, and they study
me, for they have divined that I may be coming their way. And so their
studies and researches continue, into the means of spinning webs between
the worlds, for they would like to catch me, as I come dreaming and
flying by.

And on that planet, I can already see their distant gray mountains, with
their grinding rivers of ice, and their pleasant hills and groves. I see
their mysterious oceans. I see their soft blue bowers, calling to me.
And I feel such desire that I wonder if I should go and be born there,
into their world and their species.

But is that world pulling on me, or am I fleeing this one? Did I ever
choose this world, and if I did, did I choose wisely? Or for me, was
there never a wise choice. Or is my lot forever the desolation of going
nameless up and down the streets of other minds?

Do your minds touch mine? When I speak of my emptiness, does it touch a
hollow within your hearts? Is my sorrow a sorrow to you? And is my
death, a death?
