Whahoa!! The crowd roared in approval, as the first orator rose up into
view through the mists of the river, turning slowly so all could see
her, and raising her arms in benediction.

``I come before you, quivering with self-abnegation, in a sulky
haze\ldots{}''

Bobnogar turned to her companion, with a look of delight in her eyes.
``The grand old style! How delicious, the beginning of the golden
afternoon's perorations!''

Kratnik nodded, beaming. ``Oh, my words and whiskers! They're off to a
great start. Oh, be still, my heaving bosom!'' And she put her hand
there, on her rising and swelling blouse, to hold the black, glowing
amulet there. It wriggled in her grasp.

The speaker continued, ``... I speak in plenitudes, and what I say, I
say again and again. I have never subdued myself, afraid to say out loud
the clamorous rolling thoughts and phrases that have been presently
gathering wool and gravitas in my lofty cranium. I shall speak with the
clanging tongues of bells, those sonorous brass clappers, to bring to
mind the leathery flapping of tacos, having shed their muy deliciosas
fillings and now flying in the wind\ldots{}.''

``My glorious Kratnik, did you by any chance bring any chimichangas, in
that basket?''

``Alas, I did not think in precisely that vein. I have a fiery blue
wine, and portis berries, and pupusas, and a growler of an imperial
stout, and an arugula cilantro salad, and crumpets with jam. And your
basket?''

``Kratnik, I have tears in my eyes, hearing of what you have planned to
regale ourselves with. I have pickled okra, and a selection of radish
and cucumber kimchi, and kumquats in yogurt, and dragon fruit, and yassa
chicken with rice, and sardines in spicy tomato sauce, and banana
blossom stew, and a growler of ale.''

The speaker was continuing - ``...So join me, in a rolling, stumbling,
manner, all of you, however feeble and halt, however circumspect,
however swathed in rectitude, join me to lurch forward into a lurid
dawn, as your fellows fall around you into the furrows of a half-plowed
barren field\ldots{}''

``Here, I'm opening the growler of stout. We'll start with that, shall
we?''

``Ah, yes. Wisely done, wisely done. Is there anything that can compare
with a growler in the grass, among friends, surrounded by the multitudes
similarly caparisoned, in a sea of adulation?''

The crowd roared - ``What,'' said Bobnogar, ``that must have been a
particularly spicy phrase or choice bon mot. Did you catch it?''

``Do you remember Loweena, how she always said''Bon Mott``? She just
liked saying it that way. I'm sure she knew that it's French, but she's
just stubborn. Would make a good tech start-up CEO, I always thought.''

``Just being stubborn and stuck on yourself does not make one
qualified\ldots{}''

Kratnik sighed. ``And yet\ldots{} look at the evidence - all around us,
all those ponderous insufferable pricks \ldots{}. Well, forget them,
let's eat some stuff.''

``Dream-facing!'' roared the speaker. ``Let us have the strength to
grip, to gasp, to flap and writhe in the cold rushing rivers, where we
interlace ourselves into the underpinnings of infinity, rushing upward,
upstream, past the ponderous jowly jaws of ravenous bears, dreaming of
the forest streams where we were born, swimming and swooping,
leaping\ldots{}''

"Do you still dream, Kratnik? Not just dream, but dream big, like when
we were young, with possibilities and powers and vistas opening up?

"Dream? Dream? This is the dream - all this... Look about you, we did
this... Don't chase phantasms. Come, take my hand, Bobnagar. Hold my
hand, close your eyes, and breathe, slowly... yes, like that. Breathe in
this golden day. Hold my hand, and breathe."
