``You \emph{asked} for it?'' His fists slowly clenched and unclenched.

``Yeah!'' She stood with her feet apart, braced. Her eyes glittered.
"What I've been wishing for \ldots{} for months and months. Wishing on
candles. Wishing on first stars and all that crap.

``\emph{Why}, Barrett? You could have looked it up; petitioned one of
the Libraries, or asked someone. You didn't even use a mirror!''

``\emph{You} told me the mirrors were no protection.'' Her tone was
venomous. ``And I \emph{did} ask someone.''

``You asked one of \emph{them}.'' His voice flattened.

Wisps of hair wafted to either side of her neck in the air currents from
the enormous, dark-patterned wings slowly opening and closing behind
her, bright deltas netted with tributaries of shadow.

``You're just jealous!'' The hard glitter in her eyes had become
brimming tears. ``You and all the other \emph{adults} \ldots{}'' Her
face became a caricature of maternal solicitude. ``Barr-ee, don't look
for Blessings---you might find one. Barr-ee, don't talk about the
Blesséd, or they might come.'' Her eyes narrowed. ``But they never came
for any of \emph{you}, did they?''

``No one \emph{wanted} them to come! Barrett, you heard the
stories\ldots{}. How could you---anyone---want such a thing?''

She was openly sobbing now. ``Then why do you call them Blesséd?''

He was silent for a moment. ``It's because people were afraid, Barry.
Don't you understand? It's just superstition. They thought it was a sort
of protection. Like they used to call fairies `Good Folk'; or the
Furies, the `Kindly Ones.'\,''

The wings hesitated, just for a moment, then resumed their slow stroke.
``Are you afraid of \emph{me?}''

``You have to go, Barrett.''

``Are. You. Afraid. Of me. \emph{Say} it!'' Her voice rose into a
shriek.

``Not for me. For the other children.'' The droop in his shoulders, as
if weighted down by an invisible, inescapable burden, seemed to drag
down the corners of his mouth.

``I--- I'll cut them off!'' She looked around behind her wildly from
side to side, as if trying to read directions or authorization in a
language imprinted on the mottled feathers. But her nails were already
starting to lengthen, taking on a metallic darkness.

Far overhead, so high that they were only pinpricks of despair
distorting in and out of visibility, a squadron of them was waiting for
her, lazily spiraling in the gyre of winds.

first appeared in \emph{Tidbits}
