I had hidden among the dark trees and thick undergrowth at the top of
the hill since just before sunset. Now the stars were coming out,
despite the glare of streetlights and shopping plazas from the town
below. It was a school night, so the kids were getting an early
start---I hadn't needed to wait long. Evening dew was already misting
the dead leaves under the high, cold light of the cosmos. I had never
wanted anything but peace and quiet in my life, nor had I ever been the
violent sort. Fate plays odd tricks on us sometimes.

As the cars parked one by one at a discreet distance from each other, a
beginning throb of unnatural lust was not welcome, even though it warmed
me. Once again I felt myself being tugged forward by what I desperately
wished to dissociate myself from. \emph{Not me! Not a part of my body}
... What had I done to deserve this? Why was I afflicted with such
horrible desires?

I waited until the car farthest beneath the shadow of the forest canopy
began to rock gently. A quick glance at the other vehicles showed their
occupants' attention was equally focused on private matters. My skin
tingled with heat, but all the energy seemed to focus on a specific part
of my anatomy. Though I had thought many times of removing it, I was not
strong enough---the half-hearted attempts using household implements had
been too painful for me to persevere.

I crept along the ground, snaking silently through the bushes. My
clothes were stained dark with age and use, and my skin was naturally a
dark shade; I would have appeared no more than a moving shadow cast by
the branches overhead. Sharp pebbles bruised my knees, and the heel of
my hand was punctured by thorns, but the pain could not prevent me from
going forward; I had almost completely lost voluntary control of my
muscles. As I approached the passenger side of the car, I noticed a
patch of mud gleaming on the ground just below the door. \emph{Perhaps
there} is \emph{a way to end this, after all.}

I diverted my trajectory slightly, so that my left hand and knees
plunged into the gooey muck. As the terrible hook that had replaced my
lost right hand reached for the door handle, my body began to climb to
its feet, and---as I had prayed---slipped in the mud. I fell against the
side window with a heavy thump; for just an instant, I was merely a dead
weight, my face and the hook clearly visible through the glass. A siren
shriek rose from within, then the noise of terrified scrambling, and the
locks clicking shut.

Before I could rise again to a standing position from the slippery
footing, the engine caught with a roar. The car reversed rapidly in a
half-circle, my hook firmly caught in the door handle. I could have wept
in disappointment when, without my conscious volition, my muddy,
dripping left hand also took hold of the handle as the car shifted into
forward gear and shot away. But as the accelerating car gyrated down the
gravel fire road, swaying wildly from side to side as it bounced on the
bumps and potholes, the ooze coating my left hand made a secure grip
difficult to maintain. Finally, the car sideswiped a small sapling, and
my enslavement was over! I watched the tail-lights disappear downhill as
a faint and festive jingling came from the detached, demonic metal hook
dangling from the car door.

I thrust my stump high aloft in exultation. \emph{Yes! Free at last!}
There was little bleeding or oozing. I looked about for another car
containing a friendly young couple who could be prevailed upon to
disengage long enough to take me to the emergency room. They would be
safe; it was only the hook, the horrible hook, that had inflicted the
obsessive perversions I had felt compelled to pursue.

The constellations were still brightening overhead, and a meteor flashed
briefly across the sky. Over countless eons, some of those shooting
stars and their fragments had fallen to the planetary surface, sources
of rare, elemental metals that, originally, could not be mined by
humans. Who knew where and how the endless cycle of their forging and
reforging into weapons, tools, and machines might have ultimately caused
those metals to be employed? Coming from the unutterable reaches of
space, what hideous entities might have sent them, for what nefarious
purpose?

This time, I vowed, no metal bits \emph{anywhere} in the
prosthesis---just nice, inert, flesh-colored plastic. Even if it didn't
at all match the actual greyish-black hue of my decomposing skin. And
then back to my happy, routine existence. With luck, there would be some
rotting surgical remains in the dumpsters behind the hospital after I
was discharged; otherwise, there was never a shortage of roadkill. The
thought of eating fresh, \emph{living} flesh was disgusting: I was back
to normal again!

first appeared in \emph{Weird Mask Zine}
