\emph{It took me years to become this.}

To become \emph{what?} You live in a half-burned-out trailer in the
woods. You don't even have a job or a car anymore. Christ, you're not
safe on your own.

\emph{I studied leaves by day and stars by night. In winter I studied
the light on snow. On cloudy nights I studied the memory of stars.}

If by "studying" you mean drinking that homemade hooch you call
moonshine and looking out the window, yeah, I guess you can call that
studying. If you had a TV at least you might learn something. This
herbal tea you made is really crappy.

\emph{I went into myself and out the other side, and I went on.}

You mean that bad acid trip or whatever when you spent a month in the
county mental hospital? Good thing the state picked up the tab. That
shrink, Dr.~Chandra? She seemed worried about you. You're still seeing
her, aren't you? Aren't you?

\emph{I opened a path for others. I lit lamps and placed them along the
way.}

Yeah, they were \emph{really} happy about the fire. Lucky for you they
decided it wasn't worth pressing arson charges against someone already
in a mental hospital. Too bad the middle school wouldn't give you back
the janitor job.

\emph{Here, the door is always open, and the light of the lamps shines
through.}

I'd keep that door to the burned part shut if I was you; it really
stinks in there. I think some kind of animal got in; I can hear 'em
rustling around. Vermin. And I told you a zillion times those kerosene
lamps aren't safe. To say nothing of trying to heat a house trailer with
a woodstove. I don't know why I bother. When are you going to grow up?

\emph{Our guests cannot enter without invitation. I greet them at the
threshold.}

You're not taking your meds, are you? Nobody comes here except me, and
you're lucky I promised Ma and Pop I'd take care of you. I brought you a
bunch of stuff that was on sale 'cause it got freezer-burnt. Come to
think of it, I never got you tea, though. Was it left over from before?
It wasn't leaves you picked in the woods, was it? What was in that tea I
drank?

\emph{Welcome them to our world, sister.}

The door is standing open. Whose clawed fingers reach through? It's
getting dark too soon.

first appeared in \emph{Eschatology}
