\chapstory{F. J. Bergmann}{OPERATION TO DISSEVER SOUL FROM EX-GIRLFRIEND’S SOUL SUCCESSFUL}

BALTIMORE, MD -- An elite surgical team at Johns Hopkins successfully
detached the soul of Ed Poe, 27, from that of his former girlfriend,
Anna "Belle" Lee, 22, using a revolutionary new technique. The operation
had previously been attempted by divine and infernal means, but both of
those efforts failed.

Pale and wan but smiling after the 14-hour ordeal, Poe said from his
hospital bed, "I'm feeling lots better than I expected! I've always
been, like, a pessimist, so I anticipated that my soul from out that
shadow would be lifted nevermore, like when Lenore broke up with me."

Poe claims to be experiencing "a real sense of relief and lightness."
Lee was discharged by the hospital into the care of relatives
immediately following the operation and could not be reached for
comment. Poe, an avid corvidologist, keeps a tame raven, and was
concerned that the neighbor's children he had hired to care for his pet
during his hospital stay might not be mature enough to handle the
responsibility. "I'm sure they mean well, but they have been known to
forget to leave the window open so Khalil can get in when I'm not there
to hear a rapping, as of someone gently tapping, and a couple of months
ago I caught them trying to teach him rap from old Puff Daddy YouTube
videos. How many times do I have to tell them that 'Nevermore' is
traditional?"

Poe intends to go on the lecture circuit after he recovers. "I feel that
I have a lot to offer, especially as inspiration for those poor souls
trapped in toxic or high-maintenance relationships. I mean, like, now
that the nightmare is over, I can't believe that I actually spent every
night by her side, in a tomb! The Goth thing is so not me."

Poe is looking forward to resuming alcohol and opium use as soon as his
doctors give the OK.
