\chapstory{F. J. Bergmann}{Mirror}

\lettrine{T}{hey called it} Little Mirror on the county maps. It didn't show up on
the state maps, ever. It was way out in the back woods on my
grandfather's farm, 640 acres until everything got busted up and went to
hell in the Depression. The land was junk then, too; never did any good,
too wet and sour. The water showed up as a round circle on the old
township map, \emph{Little Mirror Lake} in that fine script next to it,
but the real shape changed every year, like a reflection in a carnival
funhouse. As the years filled it in, the marsh spread and the tamaracks
rotted and fell. I heard it's public wetlands now.

When I was just a kid, I found a small round mirror along the state
highway once, probably out of some lady's makeup bag, and I carried it
around in my pocket. Still got it. At night, after Dad had drunk enough
so I could be pretty sure he wouldn't wake up and come into my room, I'd
read with a flashlight under the blanket about others, out there in
space, and I felt more like them than like me. I started signaling every
clear night, using the mirror to flick a code of flashes at the black
sky, way faster than I could thumb the flashlight's stiff, clumsy
switch, hoping somebody might see the pattern and recognize a distress
call: \emph{Get me out of here.}

The noise wasn't as loud as you would have expected. I heard it, in the
quiet backroads night, but I don't think anybody else did, except our
dog. Rusty howled for days, till Dad kicked his ribs in and he died. Dad
always said my mom ran off with some man when I was little. I can't
remember her at all. The trees were thick back then around the shallow
bowl of the lake. Nobody else ever came around; Dad kept Grandpa's old
shotgun loaded with rock salt. I never had much luck with friends, even
after Dad had the accident with that same gun.

I had paths through the brush where nobody'd follow me, and I went
looking the next day. It didn't take long to find, with the broken
branches and torn-off leaves, but the ship had slid into the undergrowth
quite a ways. Nobody could have seen it. It wasn't shiny anywhere at
all, but wrecked and burnt black, and pitted with holes like canker
sores. The door was open, but there wasn't any light and it smelled
funny. I never went in there, it didn't seem right. There used to be
water lilies at that end of the lake. That ship didn't look big enough
to hold more than just the one, anyway. The ground was too soft to plow,
and that scrub grows fast if you don't bushhog it.

He'd made it as far as the edge of the lake, and was lying half under
where the water opened to reflect the sky. I think it was a he; the
shell around the middle might have been skin or clothes, I never tried
to open it. His surface was slick like a frog, except where the sun had
been hitting him, and the part of him that was torn open was in the
water but wherever the water met his body the beautiful colors were
already leaching and faded. There was a couple of dying bluegill on the
bank. They never were worth the eating, anyhow.

Not much more dark liquid, rusty, came from the wound when I lifted him.
It smelled like copper and lightning. Where I touched him my fingers
burned and oozed but they finally healed and you can hardly notice the
marks anymore. He wasn't heavy at all, and I didn't see any metal. He
was smooth, like horn or plastic, kind of spongy underneath. Not so
different from anybody else, as far as I know.

I held the mirror to the opening in his face for a long time, but it
stayed clear and dark. Then I slid him the rest of the way into the lake
and he drifted down into the black mud and was gone, under the
glittering mirror. I put him in the lake, he was trying to get there. On
the surface were only the water lilies, hanging in an upside-down
heaven. I never dumped anything into that lake that didn't belong.

\appearedin{Newport Review}
