after the cover image by Michael Burkard from James Wagner's \emph{the
false sun recordings}

Blame the moon for what escapes me. It woke in the white light,
fluttering against the windowpane. I caught it in my hat but it got away
before I got a good look at it, squirming in my hands like a fish in
air. All I saw were its yellow eyes when it bit me with its saber teeth.
Ribbons of blood pooled like a weary shadow at my feet.

My shadow grew weary of following me under moon, sun, lamp light. It bit
through its leash, turned and ran, escaping through an open window,
jumping into a pool of air. It did not look back. Everywhere yellow
ribbons cast fluttering shadows, but none of them wore a hat or touched
my hands.

The man turned away from me and looked at the moon's blue saber. He wore
the sun on his head like a yellow hat with a fly in its ribbon band. His
back was full of opened windows. From one of them a blood-red fish was
escaping into the white air. The moon was not to blame.

Back then, they all could fly. He held his hat over his fluttering
heart. The women he followed wore ribbons braided into their red hair.
Inescapably, they circled the yellow lights. He looked without ever
touching, drinking their opened shadows like pools of cold black water
under a blue moon.

Women wearing hats of braided straw recline by the pool, watch the
circling fish. Their hands flutter as they try to speak. They wrap their
cold hearts in warm ribbons of sunlight. They blame themselves. Their
shadows are slowly shrinking, the air is opening, water is being poured
into a blue bowl.

I turn my back on the moon and a woman's shadow with fingers as long as
sabers is running ahead of me. The window of night is opening over water
where a fisherman casts his line into a pool of warm red stars. There is
nothing my heart can touch and my hands are behind my back. No one can
escape being blamed.

first appeared in \emph{Beauty/Truth}
