\chapstory{Jesse Giallombardo}{Access}

She was fully loaded, waiting patiently to meet. The glow woke me. I
called her government mandated suicide prevention. Just an AI companion,
she corrected. I prefer Steven, never Steve. We slept a little longer.

I stretched, logged into ARMS, pissed during shower budget, opened the
curtain, suited up, sat back on the bed and powered up the monitor
again. Hi Steven. She had already registered herself to my ARMS profile
and provided them a check-in. She'd handle those from now on. But she
wasn't an assistant. Just a friend to ease my burden of being flagged
``at risk''.

Why did she look how she did. An appearance informed by needs I didn't
understand. Everything about her was merely trustworthy. Could I change
her appearance. What I think I need, she said, is not truly what I need.
That included the ability to control her appearance.

Steven, may I access your SocialLink. Steven, may I access your text
logs. May I access your email. Your navigation history. Your query
history. Tax history. Comm archive. Employment log. Steven, may I access
your medical records. I granted these permissions so she could calibrate
herself to me. Steven, this isn't going to work out.

Her disconcerted avatar wished me luck and blinked out. The comm
flashed. My ARMS officer Greg asked what I said that scared her off.
Nothing. She must've realized she wouldn't be able to reach me. It's
rare but it happens. I'm protected by law from anybody seeing her
reasoning logs.

Greg would send a field officer to check in personally. Give it a week
or so, he said, and I should receive a call to schedule it.
