The fields were quiet now. It was a relief to Janie, not having the
constant knowledge that their meticulously designed miniature empires
were inexorably moving toward death throes. Even though the dying was
limited to species that were not sentient, (as far as they had been able
to ascertain), she found that it weighed on her. She felt their
desperation, their panic, their pain. It never built up gradually, as
one might expect. No, the discomfort that accompanied the final
population blooms that spelled the end was limited to a tiny fraction of
the total history of that world. If the timeline was reduced to one
hour, the apocalypse would take less than a minute -- fifteen seconds,
or so, really.

But after the first trial, Janie knew what to expect, and her anxiety
lasted quite a bit longer.

As the third round of testing reached critical mass, she went to the
ship dispensary and described her symptoms to the pharmacist, who
prescribed level 3 anti-anxiety bracelets. She was still wearing them.
They were the same kind the dolphins inhabiting the waters surrounding
the research continents were fitted with. Even though the dolphins had
barely failed the sentience tests, they obviously suffered during the
final trials. Now that they had finished their research, moving beyond
the third apocalypse, Janie should be able to remove the bracelets -- or
at least most of them.

She invited me to visit their ship and write a piece about their
post-apocalypse research. I found her to be refreshingly candid, if
somewhat fragile, regarding their findings. After three rounds of
documenting the rise and fall of life webs within a closed habitat, the
data indicated that once the web of life within a prescribed world
failed for the third time, there were not enough surviving organisms to
withstand the toxic residue, at least not for a long enough period to
allow dissipation of the toxins so that regeneration might occur,
beginning again the lengthy process of evolution. Three strikes and
you're out, so to speak.

I asked her how they had ascertained that the primates at the top of the
food chain on this planet were not sentient. ``That's a good question,''
she began. ``I have had my own misgivings from the start. When the
planet was first chosen, shortly after our initial arrival, there were
no primates and all other species failed the tests for sentience. After
additional evolution, though, dolphins developed tendencies that are
often precursors of sentience, and primates appeared. They were
omnivorous, thereby failing that test for sentience, however, they did
show signs of developing sentience between periods of extensive war. I
argued that with only limited guidance, they could become sentient. My
arguments were taken under review, but the outcomes of the research were
deemed too valuable to sacrifice for the questionable possibility of
developing one more sentient species, so the research continued.''

Frowning at this, I found myself siding with Janie and the omnivores on
the issue of sentience. ``If being omnivorous was the only criterion
keeping them from passing, couldn't at least a few plant-eaters be
found?''

``Yes, but there were other criteria that strengthened the argument for
their lack of sentience. They learned to build bombs and chose to use
them. They learned to harness renewable energy but chose to keep that
knowledge buried for as long as they could. They learned to educate,
feed, and heal their wealthy, but chose not to do the same for their
poor. They proclaimed themselves to be stewards of their planet's other
species while eating them, destroying their habitats, and exploiting
them into extinction.''

``Even so, with a little help, couldn't they have changed their ways?''

``We provided a variety of religions that all laid out the importance of
respect and compassion and promised terrible consequences for those who
did not abide by their teachings, but they never really caught on with
the mainstream of the species.''

Janie shook her head, shrugged her shoulders and sighed. ``I would have
loved to try one more round, giving them just a bit more guidance, but,
alas, their third trial is finished. I am definitely going to try to get
permission to do things differently on the next planet, though.''

She threw her bracelets in the recycling receptacle.
