\chapstory{Julie Fitzpatrick}{Bad Day}

After three hours at the DMVAl felt like twisting the head from
something. Anything. Instead, he heaved himself into the passenger side
of the rusted truck and bit his tongue to keep from biting off Heydra's
head.

``Everything go OK, Darlin'?''

After a couple of seconds, Al managed to shake his head, once.

Heydra wisely did not repeat the question. They pulled into traffic and
accelerated toward home. Waves of heat distorted the road ahead, but the
sky was cloudless, the sun relentless. Rattling in the back reminded Ed
that the broken water pump was not going to fix itself when they got
home. He closed his eyes and wished himself back in the city, cracking
open a Bud after a mind-numbing day at work. ``I'm sorry.''

Heydra's eyes swiveled toward him, then back at the road. ``What?''

``I'm sorry I dragged you out here. Sorry we threw away our perfectly
good life to come to this Godforsaken hick of a town where they can't
even renew a driver's license without rubbing your nose in the fact that
you weren't born here. You're an `outsider.'\,'' He made air quotes.

``Do you want to talk about it?''

``No.'' Al looked out the window at the horizon, turning a deep rose, so
unfamiliar, yet beautiful. ``I didn't show up on the photo they took for
the I.D., so they couldn't figure out what to do. It took them that long
to figure it out. They had to message by satellite and wait for a
reply.'' He shook his carapace in disgust. ``By satellite.'' Where the
fuck are we, in the last century?"

``Al,'' crooned Heydra in the most dulcet tones she could dredge up this
late in the day, ``you know that we all do the best we can with what we
have, and these\ldots people are no exceptions.''

Al concurred with a low rumble. He allowed his torso phalanges to splay
slightly, enough to release pent gases. Heydra did the same. The cabin
of the truck filled with a hazy golden mist that they both found
calming. No more was said for the rest of the trip home.
