\chapstory{Julie Fitzpatrick}{An Invitation to Eat Sunshine}

``Welcome, friend. Let us share a story before dinner.''

The miorab, a member of this planet's most social species, has invited
me to dine. It is of similar build to a human, although somewhat larger,
with more prominent features, more teeth, more hair, more muscle. We sit
opposite each other, with several unoccupied tables around us.
Extravagant gestures and expressions accompany its recital.

``Tiny, ancient grandmothers, curled in cells of collective memory,
disturb my slumber.

``My ancestors haunt my nights as ancient annals of early civilizations
fill my days. Torn from dreams by the scent of meat, I resent my salivation.
I suspect where our path went awry.''

It pauses for effect, searching my face intently, wiping the corner of
its mouth.

``Flesh born in the womb's darkness eternally seeks light---craving
renewal through devouring.
Flesh born green catches light; walling its golden treasure within its
cellular heart.
Which am I to eat?'' It looks through me, eyes distant. The question is rhetorical. I become
uncomfortable.

``Inside me, free radicals rampage, killing indiscriminately.
But sometimes, victims are only maimed.
Robbed of their functionality, these injured cells transform.
They writhe---scarred, distorted, struggling to find new purpose.
They wait for me to eat flesh born of the womb.
They wait for the dark flesh to stumble into them in its misguided quest
for light.
They would absorb the dark flesh and add its nourishment to their fresh
agenda.
They would grow---a competing colony that would battle my healthy cells.
I would become sick and die.''

It turns to me with renewed conviction. I relax, fractionally.

``I choose to eat sunshine. I eat only flesh born green now.
It does not seek light. It gives up its golden treasure gladly,
Leaving maimed cells undisturbed, until they wither, starved.
I bask in the resultant inner glow of energy, well-nourished.
My ancestors rest, and my sleep is dreamless.
I awaken joyful, resilient, refreshed, ready to live in peace and
harmony.''

It reaches across the table and envelopes me in a bone-crushing embrace.

I struggle for breath, regaining my seat upon its release.

``I feel the joy of daily experience urging me into song and recitation.
I wonder that such a simple choice can precipitate this abundance of
gladness,
Reminded of the small but significant difference between breathing and
not breathing.''

Its glance strays toward the entrance to the dining area. A tiny
expression of disturbance flits across its face.
``Ah, finally! Our food is arriving!
I revel in the bounty of sunshine on these platters! Such luscious
offerings!
Let us attack this succulent rainbow being laid before us,
And let us not delay, as I had expected to be finished eating before our
friends arrive.''

My puzzlement prompts its explanation: 
``Should the others choose to join us for a meal, I cannot guarantee your
position at the table. You may end up on it, rather than at it.''
