I descended slowly, with great majesty, I thought, surveying the scene
for demon traps, observing my summoner with interest. I don't get out
much anymore. Interest in Demons has waned in the last couple of
centuries. There are aficionados, of course, but only a very few
individuals willing to invest the time and sweat to learn the summoning
steps with the rigor needed to succeed.

It felt good to be visiting the earthly realm again. I looked forward to
a rewarding possession of this novice to the netherworld. Hmmm. Muscular
build, abundant red locks, patchouli scent, lilting voice - yes, I could
get used to possessing this form. Gathering my rising excitement and
channeling it into power, I searched for the blood sacrifice that would
grant me entry into the body through her sin. Where was it? I saw the
chalice, the fire, the herbs. Her words had been compelling, authentic.
But the blood.\ldots{}THERE WAS NO BLOOD!!! My anger knew no bounds. I
wanted to enter this pretender with violence and stay for millenia, but
it was not possible without blood. I searched for a way to repay this
deceit, circling the room as a dark tornado of energy.

She watched me with a serenity that multiplied my fury ten-fold, and
when I had reached a point of rage that defied my reason, she lifted a
clear carafe in invitation, invoking a spell of containment so pure, so
innocent, I could not resist the urge to possess the fragile bottle and
shatter its pieces to every corner of this dwelling, killing the
summoner in the process. I entered it with the smoothness of an infant
leaving the womb, my libido, and anger both instantly cooled as I heard
the thud of the stopper being jammed into the bottle's neck. Why had the
bottle not shattered?

I strained against my prison, peering out through a thick, cool
shatter-proof substance. Her muffled voice penetrated my shock as she
explained, "It's a new world, Demon. We respect all living things, now.
We don't sacrifice each other for our own benefit, and we delight in the
light of education, not the darkness of ignorance. When my child is
ready to be born, I will give you the chance to forsake your ways and
dwell on the earth as mortal. Until then, you may remain in that plastic
syrup bottle and contemplate this new world."

There was a computer monitor within my view. It flashed images that were
new to me. If I strained, I could hear the audio. My hell was not
complete, then.
