\documentclass[letterpaper,12pt,oneside,openany]{memoir}
\setulmarginsandblock{3.5cm}{3.5cm}{*}
\setlrmarginsandblock{2.5cm}{2.5cm}{*}

%\checkandfixthelayout[fixed]
%\checkandfixthelayout[nearest]
\checkandfixthelayout


\input{settings.tex}

% Ebook-style stuff: graphics and links
\usepackage[linktoc=all,hidelinks]{hyperref}
\usepackage{incgraph}

% Don't do facing page stuff
\renewcommand{\cleardoublepage}{\clearpage}


% Hack the TOC to be more flexible

\setlength{\cftbeforepartskip}{1.0em plus 0.5em minus 0.5em}
% default is 1em plus 0pt
\setlength{\cftbeforechapterskip}{1.0em plus 0.5em minus 0.25em}
% default is 1em plus 0pt

\begin{document}
\pagestyle{empty}


{
\clearpage
\null\vfill

\begin{flushleft}
{\small
\textit{Black Gardens and Other Stories}

\textlcsc{Utilitarian Universalist Press}

© Daniel G. Fitch 

\bigskip


LICENSED CC BY-NC-SA 4.0 \\
This electronic book may be distributed and/or modified under the conditions of the Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License available at:
\begin{chatlog}
https://creativecommons.org/licenses/by-nc-sa/4.0/
\end{chatlog}

This book was typeset in \LaTeX\ with the Charter BT font and the following packages:
  memoir,
  censor,
  tikz,
  lettrine,
  microtype,
  csquotes,
  amssmyb

But who knows what it looks like in your e-reader! You're the typesetter, now.

\bigskip

You can find free ebook and PDF versions of this book on the web, or find out how to buy a physical copy if you like:
\begin{chatlog}
http://danielgfitch.com/blackgardens/
\end{chatlog}

\bigskip

WHAT IS THOUGHT?!?

}


\end{flushleft}
}


%\setcounter{page}{0}
\frontmatter


\mainmatter
%\sloppy
\raggedbottom

\pagestyle{plain}


\input{prologue.tex}

\input{part1.tex}
\input{ch1.tex}
\input{ch2.tex}
\input{ch3.tex}
\input{ch4.tex}
\input{ch5.tex}

\input{part2.tex}
\input{ch6.tex}
\input{ch7.tex}
\input{ch8.tex}
\input{ch9.tex}
\input{ch10.tex}

\input{part3.tex}
\input{ch11.tex}
\input{ch12.tex}
\input{ch13.tex}
\input{ch14.tex}
\input{ch15.tex}

\input{ack.tex}

\input{andotherstories.tex}
\input{over.tex}
\input{totem.tex}
\input{body.tex}
\input{elves.tex}
\input{tothetrees.tex}
\input{halves.tex}
\input{ashes.tex}
\input{insuits.tex}


%\book{Probably Not}

%\input{gospel.tex}
%\input{tenwords.tex}
%\input{leaves.tex}
%\input{insects.tex}
%\input{portraits.tex}
%\input{gaze.tex}

\input{about.tex}

\chapter*{The End of the EPUB}

Whoa. You scrolled all the way to the bottom of this book.
You deserve a snack. That was probably hard work!

Here, I don't have a snack, but I'll make that web site link an actual link to make it easier to click. Hmm. How does this work?

\begin{chatlog}
  \href{http://danielgfitch.com}{hey kid, I'm a computer}
\end{chatlog}

Wait, no. Not quite. Uhh, here we go:

\begin{chatlog}
  \href{http://danielgfitch.com}{http://danielgfitch.com}
\end{chatlog}

YESSSSSSSS. INTERNET.

\end{document}

