\input{settings.tex}

%%% BEGIN DOCUMENT

\begin{document}
\pagestyle{empty}

\mainmatter
\raggedbottom

{
\null\vfill

\begin{flushleft}

{\small

{\variexfont{}Unstable Orbits}

© {\tubefont{}Speculative Technologies}

\bigskip

Typesetting: \emph{Dan Fitch}

Layout: \emph{Dan Fitch}

Eyeballs: \emph{Your Very Own}

Cover Art: \emph{Skinny Gaviar}

\bigskip

LICENSED CC BY-NC-SA 4.0 \\
This work may be distributed and/or modified under the conditions of the Creative Commons BY-NC-SA 4.0 International License available at:
\begin{monotype}
https://creativecommons.org/licenses/by-nc-sa/4.0/
\end{monotype}

This book was typeset in Palatino with \LaTeX\ and the following helpful packages:
  memoir,
  fontenc,
  fontaxes,
  lettrine,
  microtype,
  csquotes,
  amssmyb,
  pgfornament
\bigskip
}
\end{flushleft}
}

\clearpage
\pagestyle{plain}

\begingroup%
\centering
\vspace*{24pt}
{\HUGE \variexfont {\scshape Unstable Orbits}}\\[\baselineskip]
{\Huge \tubefont Speculative Technologies}\\[\baselineskip]
\vfill\null
\endgroup


%\setcounter{page}{0}

{\setlength{\beforechapskip}{0pt}
\begin{KeepFromToc}
  \tableofcontents*
\end{KeepFromToc}
}

\vfill
\specsep{}

\lettrine{M}{ost of these stories} were written and assembled in 2020, under the pall of a global pandemic.

Are there through-lines? Perhaps, and perhaps not. We would gather, each throwing a short prompt in a pile and lighting them on fire. And yet starting from the same space, the prompts would guide us to entirely different realms.

I won't pretend to speak for everyone here, but writing is a way to come together and spin apart, to explore what makes us human and what makes us \ldots often, worse.

Here: I hope you see the specks of humanity between the degenerating orbits, and find your way through it with us.

\vspace{1em}

\hfill-- Dan Fitch, editor


\clearpage

\input{tex/F._J._Bergmann_-_Containers.tex}
\specsep{}
\input{tex/Andy_Dibble_-_One_Last_Belly_Rub.tex}
\clearpage
\input{tex/Daniel_G._Fitch_-_Enticement.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_Flying_From_This_World.tex}
\specsep{}
\input{tex/Jesse_Giallombardo_-_Access.tex}
\input{tex/Julie_Fitzpatrick_-_Beelzabottle.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_The_Reading_Room.tex}
\clearpage
\input{tex/Daniel_G._Fitch_-_Murmuring_Hinge.tex}
\specsep{}
\input{tex/Andy_Dibble_-_Blandishment.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_Harvest_for_the_Dying.tex}
\specsep{}
\input{tex/Julie_Fitzpatrick_-_Bad_Day.tex}
\specsep{}
\input{tex/F._J._Bergmann_-_The_Interpretation_of_Dreams.tex}
\clearpage
\input{tex/Daniel_G._Fitch_-_Catchcry.tex}
\clearpage
\input{tex/F._J._Bergmann_-_Mirror.tex}
\clearpage
\input{tex/Bhim_Nimgade_-_Boromilla_Calls_Us_Back.tex}
\clearpage
\input{tex/Daniel_G._Fitch_-_Superarbitrage.tex}
\specsep{}
\input{tex/Jesse_Giallombardo_-_The_Tree.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_Luc_and_Beto_at_the_End_of_the_World.tex}
\clearpage
\input{tex/F._J._Bergmann_-_Cousin_Art.tex}
\clearpage
\input{tex/Andy_Dibble_-_The_Last_Laugh.tex}
\specsep{}
\input{tex/F._J._Bergmann_-_Glossolithia.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_The_Glorious_Perorations_Picnic.tex}
\specsep{}
\input{tex/Julie_Fitzpatrick_-_Fetch.tex}
\clearpage
\input{tex/F._J._Bergmann_-_Self-Preservation.tex}
\input{tex/F._J._Bergmann_-_Transmutation.tex}
\clearpage
\input{tex/Daniel_G._Fitch_-_After_the_Image.tex}
\specsep{}
\input{tex/F._J._Bergmann_-_The_Doorman.tex}
\input{tex/Julie_Fitzpatrick_-_An_Invitation_to_Eat_Sunshine.tex}
\specsep{}
\input{tex/Bhim_Nimgade_-_Tiny_Soldiers.tex}
\clearpage

\chapter*{\variexfont{}Acknowledgements}

\begin{flushleft}
Thanks to COVID-19, for forcing us inside and making us write.
It was strange, but made possible by modern magic like Google Docs
and Zoom.


\chapter*{\variexfont{}author BiographieS}

\vspace{2em}
F. J. Bergmann is a valkyrie on horseback, eagle eyes watching.

\vspace{2em}
Andy Dibble is a philosopher-king, translating the sky.

\vspace{2em}
Dan Fitch is a no-good punk, wishing for ambiguous utopia.

\vspace{2em}
Julie Fitzpatrick is a quilter of fates, freeing the iron.

\vspace{2em}
Jesse Giallombardo is a machine's ghost, whispering to you.

\vspace{2em}
Bhim Nimgade is an eschatonic prophet, laughing at the end.

\end{flushleft}


\end{document}

